Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)

require(janitor)
require(reshape2)
require(tidyr)
require(rstan)
require(rstanarm)
require(bayesplot)
```

>>>>

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
```
